\Title

### 2016-08-18 manuscript/manuscript.tex
About the Guyana Basin and finish discussion
Fixes #35

Differences between our Moho depth model and the seismological data
(shown in Fig.~\ref{fig:sam-residuals}b)
may indicate regions where our initial assumptions
(summarized in Fig.~\ref{fig:anomalysketch})
are inadequate or where we have
failed to correct for all crustal and mantle sources.
In general, our model fits both the seismological and gravity data well
in the oceans and in the Atlantic coast.
The largest differences are seen the along the Andean Province.
These differences are likely caused by the fact that our model does not include
the subducting Nazca plate.
Furthermore, the CRUST1.0 synthetic data test (Fig.~\ref{fig:crust1-results})
suggests that our inversion method is not able to fully recover deep Moho
depths in the Andes,
even without the effect of the subducting plate.

>>>>

Differences between our Moho depth model and the seismological data
(Fig.~\ref{fig:sam-residuals}b)
may indicate regions where our initial assumptions
(summarized in Fig.~\ref{fig:anomalysketch})
are inadequate or where we have
failed to correct for all crustal and mantle sources.
The largest differences are seen along the Andean Province and
are likely caused by the fact that our model does not include
the subducting Nazca plate.
Furthermore, the CRUST1.0 synthetic data test (Fig.~\ref{fig:crust1-results})
suggests that our inversion method is not able to fully recover deep Moho
depths in the Andes,
even without the effect of the subducting plate.
In the Guyana Basin, our model is able to fit the gravity data
but differs from the seismological data by up to $\pm 10$ km with
no clear pattern for the distribution of the  differences.
A possible explanation is an inaccuracy in the CRUST1.0 sediment model
\citep{laske2013} used to correct our gravity data.
The inversion results will be biased
if the input data includes effects other than the anomalous Moho.

In the Amazon and Paraná Basins, our model fits the gravity data but
underestimates the seismological data by up to 15 km.
This indicates that a mass excess is present in the crust or upper mantle.
A body with positive density contrast whose gravitational effect was not
removed from the data during processing will make the observed gravity
disturbance greater than it would be otherwise.
This will cause the inversion to produce a shallower Moho estimate.
These discrepancies between gravity and seismological estimates have been noted
before by \citet{nunn1988} for the Amazon Basin and \citet{mariani2013}
for the Paraná Basin.
Both studies propose high density rocks in the lower crust as probable causes
for the discrepancies.
Another possible cause for the observed discrepancy in our model could be our
failure to fully remove from the data the effects of the igneous intrusions
present in both basins.
Using a sediment model for South America more detailed than CRUST1.0
might lead to more accurate results for these basins.

Greater confidence in our Moho model can be had in areas where it is able to
fit both the gravity and the seismological data.
In such places, a gravity-derived model can serve as an interpolator for
the seismological point estimates.
In general, our model fits both data sets in the oceans,
the Atlantic coast of the continent, and central Brazil.
In the Parnaíba Basin, our model has small differences with the few
seismological data points that fall inside and on the borders of the basin.
The Moho surrounding the basins continental borders is deep, following
inward with a shallower Moho, then a deeper step, and finally a shallower
part in the middle of the basin.
Recent deep seismic reflection studies by \citet{daly2014} that cross
the basin from west to east agree with our model.
The Northern border of the Parecis Basin has a deep Moho in our model that
is corroborated by a single seismological data point.
